\begin{flushleft}
\raisebox{-.6ex}{HIGHER EDUCATION} \hrulefill
\end{flushleft}

    \noindent\textbf{M.Res. \textbar\space Economics (M2)}
    \hfill
    \textbf{10/2024 - present} \\
    \emph{Paris Polytechnic Institute} \\
	Thesis: TBA \\
	Relevant coursework: TBA

    \noindent\textbf{French Engineering MS \textbar\space Statistics,  Economics}
    \hfill
    \textbf{08/2023 - present} \\
    \emph{Paris Polytechnic Institute - ENSAE Paris}\\
	Stats project: "Innovation Networks and Firm Strategies: A New Measure of Patents Blocking Power."\\
	Relevant Coursework: Advanced Probability Theory, Theory of Point Estimation, Bayesian Estimation, Hypothesis Testing, Monte Carlo Simulations, Theoretical Machine Learning, Econometrics

    \noindent\textbf{M.Res. \textbar\space Quantitative Economics (M1)}
    \hfill
    \textbf{08/2022 - 05/2023} \\
    \emph{Paris Dauphine University - PSL}\\
	Research project: "What is the Value of Privacy? A Game Theoretical Approach."\\
	Relevant Coursework: Game Theory, Mechanism Design, Public Economics, Dynamic Programming, Advanced Microeconomics/Macroeconomics, Industrial Organizations

    \noindent\textbf{Bachelor \textbar\space Magistère, Economics}
    \hfill
    \textbf{09/2019 - 06/2022} \\
    \emph{Pantheon Sorbonne - Paris School of Economics}\\
	Thesis: "Are Short Term Contracts a Stepping Stone? Evidence from the French Labor Market."\\
	Relevant Coursework: Advanced Calculus, Advanced Linear Algebra, Real Analysis, Optimization, Probability Theory, Statistics, Econometrics, Microeconomics/Macroeconomics, Economic History, Economic Epistemology
\begin{flushleft}
\raisebox{-.6ex}{WORK \& RESEARCH EXPERIENCE} \hrulefill
\end{flushleft}
	\noindent\textbf{Wisdometrics} (Freelance) \hfill Montrouge, France\\[0.1cm]
    \textbf{Data Scientist / Consultant} \hfill \textbf{01/2024  - present} \\
	Engage in freelance projects with small to mid-sized companies across Europe and North America, specializing in data science. Function as an independent consultant and collaborate with internal teams to provide analysis and solutions tailored to client needs.
    
    \vspace{0.15cm}
    
    \noindent\textbf{Telecom-Paris - IP Paris} \hfill Palaiseau, France\\[0.1cm]
    \textbf{Research Intern} \hfill \textbf{01/2024  - present} \\
	Engaged in a research project about the deployment of fiber networks in France and the micro effects it caused at the firm level. Used econometric methods to estimate causal effects of fiber deployments on employment characteristics in firms.

    \vspace{0.15cm}

    \noindent\textbf{etiLab Mines Paris - PSL} \hfill Paris, France\\[0.1cm]
    \textbf{Research Assistant} (part-time)\hfill \textbf{09/2023 - 09/2024} \\
    Collaborated actively with a team of researchers by creating descriptive statistics, data visualizations, and designing models for reports and papers covering subjects in labour, IO and trade. Worked on a research project studying the effects of mergers and acquisitions on employment quality.\\
    \textbf{Research Intern}\hfill \textbf{05/2023 - 08/2023} \\
    Worked on a topology of medium size companies and the definition of their dynamics using non supervised machine learning techniques. Wrote a literature review about geographic wage inequalities.  \\[0.1cm]
    \textbf{Data Intern}\hfill \textbf{06/2022 - 08/2022} \\
    Assisted in the public data gathering, put into production a database of french mid-sized companies and created an interactive web application for data visualisation.

    \vspace{0.15cm}

    \noindent\textbf{Narodowy Bank Polski} (Polish Central Bank) \hfill Warsaw, Poland\\[0.1cm]
    \textbf{Research Intern}\hfill \textbf{08/2022  - 08/2022} \\
    Prepared a literature review on the monetary/fiscal policy-mix during the great inflation. Worked on a VAR model explaining the increases in delivery time without price hikes in some sectors. 

\begin{flushleft}
\raisebox{-.6ex}{SKILLS} \hrulefill
\end{flushleft}

    \noindent\textbf{Programming Languages:}\hfill{Java \tbar Julia \tbar Python \tbar R \tbar SQL \tbar Matlab} \\
    \textbf{Productivity:}\hfill LaTeX - MS Office - Git - GNU Linux - Windows\\
    \textbf{Web Technologies:}\hfill JavaScript \tbar React \tbar HTML \tbar CSS \tbar PHP  \\
    \textbf{Languages:} \hfill French (native) - Polish (native) - English (C1/C2) 

\begin{flushleft}
\raisebox{-.6ex}{CONTRIBUTIONS} \hrulefill
\end{flushleft}

    \noindent Mines Paris, EtiLab. (2023). \emph{Decarbonization, Reindustrialization and Mid-Sized Companies.} (\href{https://etilab.minesparis.psl.eu/wp-content/uploads/2023/12/etilab-decarboner-les-ETI-04dec23.pdf}{\underline{french}})  